Bayesian Data Analysis, Rough Draft

### 2023-12-09 Lahman Analysis/Formal Analysis/Draft1.qmd
Rendered Figures and continued working on paper

As mentioned, Fellingham and Fisher (2017) have both considered and published their thoughts on this research question. This research question concerns predicting player home run performance using Bayesian multilevel modeling. To do this, Fellingham and Fisher (2017) used data from the Lahman data set spanning 1871 to 2008 to estimate the parametric weights for their model. Over this time frame they only considered players who had played for at least 6 seasons and who, in each of those seasons, had at least 50 AB's. They only considered seasons where the players were 18-years-old to 45-years-old.

@@

$$
\begin{align}
HR_{nip}|\pi_{nip}&\sim Binomial(AB_{nip},\pi_{nip})\\
\\
\log(\frac{\pi_{nip}}{1-\pi_{nip}})&=[\beta_{n1}\cdot Age_{ni}]+[\beta_{n2}\cdot(Age_{ni})^2]+[\beta_{n3}\cdot(Age_{ni})^3]+[\beta_{n4}\cdot(Age_{ni})^4]+\alpha_n+\delta_i
+\xi_p
\end{align}
$$

Where $HR_{nip}$ is the HR's hit by a player $n$ in year $i$ played at stadium $p$. $AB_{nip}$ is the AB's for player $n$ in year $i$ at stadium $p$. $\pi_{nip}$ is the probability of a HR in an AB for player $n$ in year $i$ at stadium $p$.

The parameter's $\beta_{n,1-4}$ describe the weights of the orthogonal polynomial for, up to the quartic, ages of players. We theorize, because Fellingham and Fisher (2017) did not explicitly articulate why, that they chose a quartic model because it has a closer fit to the data displayed in @fig-HR.By.Age.All and @fig-HR.By.Age.20to40. The properties of a squared term is that it captures the rise and fall of player's HR probability. However, the inclusion of the cubic and quartic term allow for for modeling two humps, or peaks, in a data set. This appears in @fig-HR.By.Age.20to40 where players see a peak at 27 and then their probability decreases a little, which is then followed by another peak at 31, and afterwards continues in a downward trend. This will be discussed in more depth in @sec-Model but our model, which aims to improve Fellingham and Fisher's (2017) model, does not account for the cubic or quartic effects over fear of over-fitting the age data.

The parameter $\alpha_n$ (which is $\theta_i$ in the actual paper) are the individual intercepts for each player. This parameter is the only one that Fellingham and Fisher (2017) use which takes advantage of multilevel modeling. In this modeling, Fellingham and Fisher (2017) set the mean of $\alpha_n$ to be $\mu_d$ where $d$ is the decade the player was born. That means that Fellingham and Fisher (2017) set the parameter which measures the player's "innate" HR probability based on the HR probability of other players, who were born in the same decade. This allows Fellingham and Fisher (2017) to fit make confident predictions about players who may have only played for 6 seasons because they know that their model is trained on more than 6 data points. This parameter, $\alpha_n$ along with $\beta_{n,1-4}$ represent the player specific terms of the model. That is, the parameters of the model which depend solely on the player being considered.

In contrast, the parameter $\delta_i$ represents the effect that season $i$ has on player $n$'s ability to hit a HR at stadium $p$. This $\delta$ is calculated for each season considered where $i\in\{1,…,138\}$ for the 138 seasons considered. This $\delta_i$ is calculated independent of each player so it represents the different changes that we see in HR ability over all years considered. An example of why this effect is important refer to @fig-HRByYear.

The parameter $\xi_p$ is the effect that playing in park $p$ has on the HR probability $\pi_{nip}$ in year $i$. Fellingham and Fisher (2017) decided that they want this estimate to independent of the hitter. Hence, they use no pooling or multilevel effects in the model. They estimate the effect that each park has on a player's ability to hit a HR and then add the associated effect to the players who play at that ballpark.

What makes Fellingham and Fisher's model so strange are the priors that Fellingham and Fisher (2017) chose. Disregarding that there is no justification for these priors, Fellingham and Fisher (2017) set the following priors for these parameters:

$$
\begin{align}
\alpha_n&\sim Normal(\mu_{d_n},\sigma^2_{d_n}), d\in \{1...14\}, n\in\{1,...,3735\}\\
\\
\mu_d&\sim Normal(-2.5,1), d\in\{1,...,14\}\\
\\
\sigma^2_{d}&\sim Gamma(3,3), d\in\{1,...14\} \\
\\
\delta_i&\sim Normal(-2.5, 2),i\in \{1,...,138\}\\
\\
\xi_p&\sim Normal(-2.5, 2), p\in \{1,...,222\}\\
\end{align}
$$

These priors are quite strange because they are so broad. For example, consider the priors on either $\delta_j$ or $\xi_p$. The priors state that on a logistic scale, it is normal for the decade of birth and season of play parameters to vary along the interval \[-6.5, 1.5\]. On the normal probability scale, this corresponds to probability fluctuations of about (0.0015, 0.81). Furthermore, if you only consider the means that Fellingham and Fisher have used here, then you would be left with a player who, on the logit scale, hits HR's at a probability of -7.5. On the normal probability scale this becomes about 0.00055, which is 0.055% chance any AB ends in a HR. Confusingly, this is not even close to the 2.8% that Fellingham and Fisher (2017) even noted in their paper. Surely there must be better priors than this which Fellingham and Fisher (2017) could have used since it does not seem that even they believe these priors that they have set. Coincidentally, this is probably why in using MCMC to estimate their parameters they needed to use 200,000 iterations. Likely, their model could have estimated their parameters much more easily had they given stronger priors. This is one of the areas this paper seeks to improve Fellingham and Fisher's (2017) methods.

@@

Given all the previous problems with Fellingham and Fisher (2017) mentioned above, there is an argument to be made that a simple generalized linear model (GLM) could be used instead of their complicated Bayesian semiparametric model. While it is true that a GLM could be used to predict HR's of a player it would not nearly be as accurate as a Bayesian model. Nor would it be able to as accurately capture the non-linearities present in the data. This is because the greatest strength of using the Bayesian technique is that it allows for multilevel models to be created. That is, Bayesian models allow for models to "learn" from other players and group certain players when there is not as much data available for them. In turn, this leads to better predictions about players where data is lacking. This "learning" is known as partial pooling, where the model identifies that parameters for each player (or year etc.) probably come from the same distribution but may not share the exact same estimates.

@@

$$
\begin{align}
\alpha_n&\sim Normal(\mu_0, \sigma_0)\\
\beta_h&\sim Normal(\mu_1, \sigma_1)\\
\eta_h&\sim Normal(\mu_2, \sigma_2)\\
\delta_p&\sim Normal(\mu_5, \sigma_5)\\
\xi_i&\sim Normal(\mu_6, \sigma_6)\\
\end{align}
$$

@@

In this model, we say that the $HR$'s of player $n$ follow a binomial distribution with number of trials for player $n$ in season $i$ are $AB_{ni}$. The probability of success (hitting a HR) denoted as $\pi_{ni}$ for player $n$ in season $i$. Furthermore, we measure $\pi$ on the logistic scale.

As discussed in @sec-BaseBack, there are many factors that influence player $n$'s underlying probability of hitting a $HR$ in a given $AB$ during season $i$. The first parameter which affects $\pi$ is $\alpha_n$. In our model $\alpha_n$ can be generally thought of as the term which is used to account for most player's innate ability to hit HR's. This comes from our exploratory observations of the data. In @fig-HR.By.Age.20to40, @fig-pDist, and @fit-pDistSmall, we noticed that the average (median or mean) proportion of AB's which resulted in HR's to be about 0.03. This means that about 3 in every 100 AB's result in HR's. On the logit scale, which is what our model relies on, this is about -3.5. However, we recognize this depends on the hitter which is where multilevel modeling becomes useful. Instead of simply using the average probability as our intercept, which is what a dummy variable would do in a GLM, we are able to allow our model choose an intercept which agrees with the data but can adapt depending on the player. Thus, we let $\alpha$ be normally distributed with mean $\mu_0$ (where $\mu_0$ is normally distributed with mean -3.5 and standard deviation 0.1) and standard deviation $\sigma_0$ (where the parameter $\sigma_0$ itself is exponentially distributed). By allowing $\mu_0$ and $\sigma_0$ to have their own distributions, we are able to have the distribution of $\alpha_n$ adapt to the player's specific underlying probability of hitting HR's. That is, we are able to consider what can be most closely considered their innate ability because this estimate for $\alpha_n$ does not account for other considered factors, such as age, park factors, or year played.

The next parameter we considered which affects $\pi_{ni}$ was $\beta_h$ which represents the effect age $h$, on the centered scale, has on a player's ability to hit HR's. This topic was briefly touched upon in @sec-BaseBack, where we discussed how player age can impact their their strategy and physical prowess. These ideas are well demonstrated in @fig-HR.By.Age.20to40. In @fig-HR.By.Age.20to40, one can easily see that, in general, players ability to hit HR's improves over the course of their career. As a note, we centered the the age of the all players at 30 because not only was that roughly the mean and the median, but also because it makes interpreting the $\beta_h$ easier. The value of $\beta_h$ represents how changes away from the centered age affect player $n$'s probability of hitting a HR, $\pi_{ni}$. In normal GLM's, $\beta_h$ would be general to age, meaning that there would be one intercept for each age that fit all players in the data the best. However, as with $\alpha_n$, we have employed a multilevel model to allow for each $\beta_h$ to be specific to each player. It becomes more difficult to interpret the values of $\beta_h$ because they correspond to the multiplicative effect of the centered age index. That is, in calculating the value of $\beta_h$, our model considers the priors we have set with $\mu_1$ and $\sigma_1$ to create a distribution for $\beta_h$ and then multiplies this $\beta$ with our centered age value $h$. In essence, this means that our $\beta_h$ describes the multiplicative effect of being a certain distance from the centered age, and how that effects player's $\pi$. Another important note, is that although this effect of $\beta$ is multiplicative with respect to the player's index, $h$, it is additive with respect to $\alpha$ and therefore $\pi$. This means that the whatever the model predicts for $\beta_h$ and its weight, it must be added to $\alpha_n$ to generate the correct $\pi$.

@@

```{r}
#Lets me load in the model that I made. Will only work on my desktop.
#fit.poly <- readRDS("C:/Users/Sam/Desktop/RDS/PolyFit.rds", )

#Lets me load in the model for my Mac
fit.poly <- readRDS("~/Desktop/RDS/PolyFit.rds")
```

@@

```{r}
#| label: fig-pDist
ggplot(data = Batting)+
  aes(x = p)+
  geom_histogram(bins = 75)+
  geom_vline(xintercept=median(Batting$p, na.rm = TRUE) , color="red")+
  scale_x_continuous(n.breaks = 10)+
  labs(title = "Distribution of Players' HR Proportions",
       subtitle = "Seasons Considered: 1973-2019",
       x = "Proportions (p)",
       y = "Observations")
```

```{r}
#| label: fig-pDistSmall
#I want this to have a little more breaks in the x-axis to highlight where the median is
ggplot(data = Batting)+
  aes(x = p)+
  geom_histogram(bins = 75)+
  geom_vline(xintercept=median(Batting$p, na.rm = TRUE) , color="red")+
  scale_x_continuous(n.breaks = 16, limits = c(0,0.15))+
  labs(title = "Constricted View of Distribution of Players' HR Proportions",
       subtitle = "Seasons Considered: 1973-2019",
       x = "Proportions (p)",
       y = "Observations")
```

```{r}
#| label: fig-p651Act
ggplot(data = select_player_Batting)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth()+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Actual Trajectory for player #651")
```

```{r}
#| label: fig-p651Pred
ggplot(data = select_player_Batting)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth(color="red")+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Predicted Career Trajectory for #651")
```

```{r}
#| label: fig-p582Act
ggplot(data = i582.Trajectory)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth()+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Actual Trajectory for player #582")
```

```{r}
#| label: fig-p582Pred
ggplot(data = i582.Trajectory)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth(color="red")+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Predicted Career Trajectory for #582")
```

```{r}
#| label: fig-p177Act
ggplot(data = i177.Trajectory)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth()+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Actual Trajectory for player #177")
```

```{r}
#| label: fig-p177Pred
ggplot(data = i177.Trajectory)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth(color="red")+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Predicted Career Trajectory for #177")
```

```{r}
#| label: fig-p420Act
ggplot(data = i420.Trajectory)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth()+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Actual Trajectory for player #420")
```

```{r}
#| label: fig-p420Pred
ggplot(data = i420.Trajectory)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth(color="red")+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Predicted Career Trajectory for #420")
```

>>>>

As mentioned, Fellingham and Fisher (2017) have both considered and published their thoughts on this research question, which concerns predicting player home run performance using Bayesian multilevel modeling. To do this, Fellingham and Fisher (2017) used data from the Lahman data set spanning 1871 to 2008 to estimate the parametric weights for their model. Over this time frame they only considered players who had played for at least 6 seasons and who, in each of those seasons, had at least 50 AB's. They further restricted their pool of players to only considered seasons where the players were 18-years-old to 45-years-old.

@@

$$
\begin{align}
HR_{nip}|\pi_{nip}&\sim Binomial(AB_{nip},\pi_{nip})\\
\\
\log(\frac{\pi_{nip}}{1-\pi_{nip}})&=[\beta_{n1}\cdot Age_{ni}]+[\beta_{n2}\cdot(Age_{ni})^2]+[\beta_{n3}\cdot(Age_{ni})^3]+[\beta_{n4}\cdot(Age_{ni})^4]+\alpha_n+\xi_i
+\delta_p
\end{align}
$$

Where $HR_{nip}$ is the HR's hit by a player $n$ in year $i$ played at stadium $p$. $AB_{nip}$ is the AB's for player $n$ in year $i$ at stadium $p$. $\pi_{nip}$ is the probability of a HR in an AB for player $n$ in year $i$ at stadium $p$ measured on the logistic scale.

The parameter's $\beta_{n,1-4}$ describe the weights of the orthogonal polynomial, up to the quartic, for the ages of the players. We theorize, because Fellingham and Fisher (2017) did not explicitly articulate why, they chose a quartic model because it has a closer fit to the data displayed in @fig-HR.By.Age.All and @fig-HR.By.Age.20to40. The properties of a squared term capture the rise and fall of player's HR probability over their career. The inclusion of the cubic term allows for the modeling of multiple peaks, while the quartic term allows it to maintain that overall trend up and then down seen in the data. This appears in @fig-HR.By.Age.20to40 where players see a steady increase in their HR probability during their career with a peak when they are 27. Then, their probability decreases a little, followed quickly by another increase, which then leads to another peak when the player is 31. Afterwards, the probability continues in a downward trend. This will be discussed in more depth in @sec-Model but our model, which aims to improve Fellingham and Fisher's (2017) model, does not account for the cubic or quartic effects over fear of over-fitting the age data, since the distinction between the humps is rather small.

The parameter $\alpha_n$ (which is $\theta_i$ in the actual paper) are the individual intercepts for each player. This parameter is the only one that Fellingham and Fisher (2017) use which takes advantage of multilevel modeling. In this modeling, Fellingham and Fisher (2017) set the mean of $\alpha_n$ to be $\mu_d$ where $d$ is the decade the player was born. That means that Fellingham and Fisher (2017) set the parameter which measures the player's "innate" HR probability based on the HR probability of other players who were born in the same decade. This allows Fellingham and Fisher (2017) to make confident predictions about players who may only have 6 seasons of data because this model borrows data from all players who were born at around a similar time. Implicitly, this means that Fellingham and Fisher (2017) assume that when a player was born is a powerful predictor of their HR probability.

In addition, $\alpha_n$ is not the only player specific parameter of this model. The parameters $\beta_{n,1-4}$ attempt to measure how a player's age might affect their ability to hit HR's. In contrast to $\alpha_n$, this parameter does not use multilevel modeling techniques. Instead, it relies on a more traditional statistical approach which considers how age affects players aggregately. That is, it relies on one fit for all the age data and then applying that uniformly to all players considered who are that age.

In contrast, the parameter $\xi_i$ (which is $\delta_i$ in the actual paper) represents the effect that season $i$ has on player $n$'s ability to hit a HR at stadium $p$. This $\xi$ is calculated for each season considered where $i\in\{1,…,138\}$ for the 138 seasons considered. This $\xi_i$ is calculated independent of each player so it represents the different changes that we see in HR ability over all years considered. An example of why this effect is important refer to @fig-HRByYear, which clearly shows how HR rates have differed drastically over the years considered.

The parameter $\delta_p$ (which is $\xi_p$ in the actual paper) is the effect that playing in park $p$ has on the HR probability $\pi_{nip}$ in year $i$. Fellingham and Fisher (2017) decided that they want this estimate to independent of the hitter. Hence, they use no pooling or multilevel effects in this part of the model. They estimate the effect that each park has on a player's ability to hit a HR and then add the associated effect to the players who play at that ballpark in a given year.

One of the main reasons that Fellingham and Fisher's (2017) model is so strange are the priors that they chose. Disregarding that there is no justification for these priors in their paper, Fellingham and Fisher (2017) set the following priors for these parameters:

$$
\begin{align}
\alpha_n&\sim Normal(\mu_{d_n},\sigma^2_{d_n}), d\in \{1...14\}, n\in\{1,...,3735\}\\
\\
\mu_d&\sim Normal(-2.5,1), d\in\{1,...,14\}\\
\\
\sigma^2_{d}&\sim Gamma(3,3), d\in\{1,...14\} \\
\\
\xi_i&\sim Normal(-2.5, 2),i\in \{1,...,138\}\\
\\
\delta_p&\sim Normal(-2.5, 2), p\in \{1,...,222\}\\
\end{align}
$$

These priors are quite strange because they are so uninformative. For example, consider the priors on either $\xi_i$ or $\delta_p$. The priors state that on a logistic scale, it is normal for the decade of birth and season of play parameters to vary along the interval \[-6.5, 1.5\]. On the normal probability scale, this corresponds to probability fluctuations of about (0.0015, 0.81). Furthermore, if you only consider the means that Fellingham and Fisher have used here, then you would be left with a player who, on the logit scale, hits HR's at a probability of -7.5. On the normal probability scale this becomes about 0.00055, which is 0.055% chance any AB ends in a HR. Confusingly, this is not even close to the 2.8% that Fellingham and Fisher (2017) even noted in their paper. Surely there must be better priors than this which Fellingham and Fisher (2017) could have used since it does not seem that even they believe these priors that they have set. Coincidentally, this is probably why in using MCMC to estimate their parameters they needed to use 200,000 iterations. Likely, their model could have estimated their parameters much more easily had they given it stronger priors. This is one of the areas this paper seeks to improve Fellingham and Fisher's (2017) methods.

@@

Given all the previous problems with Fellingham and Fisher (2017) mentioned above, there is an argument to be made that a simple generalized linear model (GLM) could be used instead of their complicated Bayesian semiparametric model. While it is true that a GLM could be used to predict HR's of a player it would not nearly be as accurate as a Bayesian model. Nor would it be able to as accurately capture the non-linearities present in the data. This is because the greatest strength of using the Bayesian technique is that it allows for multilevel models to be created. That is, Bayesian models allow for models to "learn" from other players and group certain players when there is not as much data available for them. In turn, this leads to better predictions about players where data is lacking. This "learning" is known as partial pooling, where the model identifies that parameters for each player (or year etc.) probably comes from the same distribution but may not share the exact same estimates.

@@

$$
\begin{align}
\alpha_n&\sim Normal(\mu_0, \sigma_0),n\in\{1,...,657\}\\
\beta_n&\sim Normal(\mu_1, \sigma_1),n\in\{1,...,657\}\\
\eta_n&\sim Normal(\mu_2, \sigma_2),n\in\{1,...,657\}\\
\delta_p&\sim Normal(\mu_5, \sigma_5),p\in\{1,...,88\}\\
\xi_i&\sim Normal(\mu_6, \sigma_6),i\in\{1,...,47\}\\
\end{align}
$$

@@

In this model, we say that the $HR$'s of player $n$ follow a binomial distribution with number of trials for player $n$ in season $i$, where player $n$ played in park $p$, are $AB_{nip}$. The probability of success (hitting a HR) is denoted as $\pi_{nip}$ for player $n$ in season $i$ playing at park $p$. Furthermore, we measure $\pi$ on the logistic scale.

As discussed in @sec-BaseBack, there are many factors that influence player $n$'s underlying probability of hitting a $HR$ in a given $AB$. The first parameter which affects this probability, $\pi_{nip}$, is $\alpha_n$. In our model $\alpha_n$ can be generally thought of as the term which is used to account for a player's innate ability to hit HR's. From our exploratory observations of the data, we noticed that the average (median or mean) proportion of AB's which resulted in HR's to be about 0.03. This means that about 3 in every 100 AB's result in HR's. This can be seen in @fig-HR.By.Age.20to40, @fig-pDist, and @fig-pDistSmall. On the logit scale, which is what our model relies on, a probability of 0.03 is about -3.5. We recognize that some players, for whatever reason, have better "innate" abilities to hit HR's than others. Therefore, we used a multilevel modeling technique for $\alpha_n$ to capture that player-to-player difference. Instead of simply using the average probability as our intercept, which is what a dummy variable would do in a GLM, we allow our model choose an intercept which adapts depending on the player and the data. That is, we give our model priors that we would expect to see in the data and then, as the model interprets additional observations, it updates these priors using Bayes theorem. For these priors, we let $\alpha$ be normally distributed with mean $\mu_0$ (where $\mu_0$ is normally distributed with mean -3.5 and standard deviation 0.1) and standard deviation $\sigma_0$ (where the parameter $\sigma_0$ itself is exponentially distributed). This allows us to have separate intercepts for each player $n$, but these intercepts come from the same hyper-priors $\mu_0$ and $\sigma_0$ that the model considers for all other players. Thus, the model constructs its posterior predictions based on both the priors and the data. In effect, this makes the model appear as though it is "learning" from the data because it has the same general sense of how a player should perform, but then adapts that prediction based on the data it takes into account to form its posterior. Specifically, for $\alpha_n$ we say that the means of all players roughly follow the distribution of $\mu_0$, but we also tell the model that it should look at how player $n$ performed to gauge its posterior prediction. A similar process is followed for $\alpha_n$'s standard deviation, $\sigma_0$.

The next parameter we considered which affects $\pi_{nip}$ was $\beta_n$ which represents the effect centered age (30 minus the player's age) had on player $n$'s ability to hit HR's. This topic was briefly touched upon in @sec-BaseBack, where we discussed how a player's age can impact their their strategy and physical prowess. These ideas are well demonstrated in @fig-HR.By.Age.20to40. In @fig-HR.By.Age.20to40, one can easily see that, in general, players' ability to hit HR's improves over the course of their career and peaks when players reach about 30 years old. After this peak, a player's ability starts to decline for the rest of their career. We chose to center the the age of the all players at 30 for several reasons. The first was that roughly the mean and the median ages of the data was at 30. And second, because having a centered age makes interpreting $\beta_n$ easier. The value of $\beta_n$ represents how changes away from the centered age affects player $n$'s probability of hitting a HR, $\pi_{nip}$. In a normal GLM's, $\beta_n$ would not be able to adapt to each player, $n$, as it does in our model. It would only be able to consider how aging affects the average player's HR probability and then apply that effect to all players. This implicitly assumes that each player is affected identically by changes in age. In contrast, we employ multilevel modeling techniques to our model which assumes that most players experience the same general effects of aging, but allows for subtle changes depending on the player. This is the job of our hyper-priors, $\mu_1$ and $\sigma_1$. The parameter $\mu_1$ acts as the general mean which we expect most players to follow. However, since $\mu_1$ is a distribution, it allows for our model to update its posterior with observed data so that it is not heavily influenced by either a few data points or our strong priors. Our standard deviation parameter, $\sigma_1$ acts similarly. Thus, we have estimates $\beta_n$ for player $n$ which describes how aging uniquely affects their probability of hitting a HR in a given AB, $\pi_{nip}$, but these unique estimates generally follow the same trend.

@@

```{r}
#Lets me load in the model that I made. Will only work on my desktop.
fit.poly <- readRDS("C:/Users/Sam/Desktop/RDS/PolyFit.rds", )

#Lets me load in the model for my Mac
#fit.poly <- readRDS("~/Desktop/RDS/PolyFit.rds")
```

@@

```{r}
#| label: fig-pDist
ggplot(data = Batting)+
  aes(x = p)+
  geom_histogram(bins = 75)+
  geom_vline(xintercept=median(Batting$p, na.rm = TRUE) , color="red")+
  scale_x_continuous(n.breaks = 10)+
  labs(title = "Distribution of Players' HR Proportions",
       subtitle = "Seasons Considered: 1973-2019",
       x = "Proportions (p)",
       y = "Observations",
       caption = "Median market in red.")
```

```{r}
#| label: fig-pDistSmall
#I want this to have a little more breaks in the x-axis to highlight where the median is
ggplot(data = Batting)+
  aes(x = p)+
  geom_histogram(bins = 75)+
  geom_vline(xintercept=median(Batting$p, na.rm = TRUE) , color="red")+
  scale_x_continuous(n.breaks = 16, limits = c(0,0.15))+
  labs(title = "Constricted View of Distribution of Players' HR Proportions",
       subtitle = "Seasons Considered: 1973-2019",
       x = "Proportions (p)",
       y = "Observations",
       caption = "Median marked in red.")
```

```{r}
#| label: fig-p651Act
ggplot(data = select_player_Batting)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth(se=FALSE)+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Actual Trajectory for player #651 - Robin Yount",
       x = "Centered Age (Player Age - 30)",
       y = "HR's per AB",
       caption = "General trend of data in blue.")
```

```{r}
#| label: fig-p651Pred
ggplot(data = select_player_Batting)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth(color="red", se = FALSE)+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Predicted Career Trajectory for #651 - Robin Yount",
       x = "Centered Age (Player Age - 30)",
       y = "HR's per AB",
       caption = "General trend of data in red.")
```

```{r}
#| label: fig-p582Act
ggplot(data = i582.Trajectory)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth(se=FALSE)+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Actual Trajectory for player #582 - Pat Tabler",
       x = "Centered Age (Player Age - 30)",
       y = "HR's per AB",
       caption = "General trend of data in blue.")
```

```{r}
#| label: fig-p582Pred
ggplot(data = i582.Trajectory)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth(color="red", se=FALSE)+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Predicted Career Trajectory for #582 - Pat Tabler",
       x = "Centered Age (Player Age - 30)",
       y = "HR's per AB",
       caption = "General trend of data in red.")
```

```{r}
#| label: fig-p177Act
ggplot(data = i177.Trajectory)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth(se=FALSE)+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Actual Trajectory for player #177 - Junior Felix",
       x = "Centered Age (Player Age - 30)",
       y = "HR's per AB",
       caption = "General trend of data in blue.")
```

```{r}
#| label: fig-p177Pred
ggplot(data = i177.Trajectory)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth(color="red", se=FALSE)+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Predicted Career Trajectory for #177 - Junior Felix",
       x = "Centered Age (Player Age - 30)",
       y = "HR's per AB",
       caption = "General trend of data in red.")
```

```{r}
#| label: fig-p420Act
ggplot(data = i420.Trajectory)+
  aes(x = cAge, y = p)+
  geom_point()+
  geom_smooth(se = FALSE)+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Actual Trajectory for player #420 - Kendrys Morales",
       x = "Centered Age (Player Age - 30)",
       y = "HR's per AB",
       caption = "General trend of data in blue.")
```

```{r}
#| label: fig-p420Pred
ggplot(data = i420.Trajectory)+
  aes(x = cAge, y=inv_logit_pred)+
  geom_point()+
  geom_smooth(color="red", se=FALSE)+
  scale_y_continuous(labels = label_percent())+
  labs(title = "Predicted Career Trajectory for #420 - Kendrys Morales",
       x = "Centered Age (Player Age - 30)",
       y = "HR's per AB",
       caption = "General trend of data in red.")
```

```{r}
#| label: fig-alphaTrace
#651, 582, 177, 420
traceplot(fit.poly, pars = c("alpha[651]", "alpha[582]", "alpha[177]", "alpha[420]"))
```
